 

### 2023-04-26 markdown/methods.Rmd
flowchart updated

@@

plot_box_setting <- gpar(fill="#DDCC77")
# input files
evidence_file <- boxGrob({glue("evidence file",
                           .sep = "\n")})
sample_annotation_file <- boxGrob({glue("sample annotation",
                           .sep = "\n")})

>>>>

data_box_setting <- gpar(fill="#56B4E9")

@@

plot_box_setting <- gpar(fill="#DDCC77")
# input files
evidence_file <- boxGrob("evidence file",
                         box_gp = data_box_setting)
sample_annotation_file <- boxGrob("sample annotation",
                                  box_gp=data_box_setting)
